### 2025-06-12 decision-making.qmd
20250612 - tweaks

- Seek advice from diverse perspectives and incorporate it into your decision making.
- Try to get opinions from others *before* you state your perspective and before the various sources of advice discuss with each other, to ensure independence of advice.
  - As noted by @Kahneman2011, "before an issue is discussed, all members of the committee should be asked to write a very brief summary of their position... The standard practice of open discussion gives too much weight to the opinions of those who speak early and assertively, causing others to line up behind them." (p. 85).
- If some sources of advice (or projections) are clearly more skilled and accurate than others, you can average this "select" crowd of projections or give them greater weight in a [weighted average]().
- If it is unclear whether or which sources are reliably more accurate than others, using a simple average across all sources (i.e., crowd-averaged projections) can be a useful approach that is as accurate as—if not more accurate than—the average individual forecaster.
- Incorporate at least 5–10 sources of projections.
Use a [weighted](#sec-descriptiveStatisticsCenter) or [robust](#sec-descriptiveStatisticsCenter) average to account for outlier projections.
- Do not bet on fantasy football (or anything else for that matter) unless you are willing to lose the money.
Sports bettors tend to be [overconfident](#sec-cognitiveBiasesOverconfidence); on average, they lose 7.5 cents for every dollar wagered [@Brown2025].
If you are going to bet, only bet a small portion of your money and never more than you are willing to lose.
And do not make multi-leg bets (parlays); people lose on average 25 cents for every dollar wagered on parlays [@Brown2025].

>>>>

- Seek advice from diverse perspectives and incorporate it into your decision making.
- Get opinions from others *before* you state your perspective and before the various sources of advice discuss with each other, to ensure independence of advice.
  - As noted by @Kahneman2011, "before an issue is discussed, all members of the committee should be asked to write a very brief summary of their position... The standard practice of open discussion gives too much weight to the opinions of those who speak early and assertively, causing others to line up behind them." (p. 85).
- If some sources of advice (or projections) are clearly more skilled and accurate than others, you can average this "select" crowd of projections or give them greater weight in a [weighted average](#sec-descriptiveStatisticsCenter).
- If it is unclear whether or which sources are reliably more accurate than others, using a simple average across all sources (i.e., crowd-averaged projections) can be a useful approach that is as accurate as—if not more accurate than—the average individual forecaster.
- Incorporate at least 5–10 sources of projections.
Use a [weighted](#sec-descriptiveStatisticsCenter) or [robust](#sec-descriptiveStatisticsCenter) average to account for outlier projections.
- Do not bet on fantasy football (or anything else for that matter) unless you are willing to lose the money.
Sports bettors tend to be [overconfident](#sec-cognitiveBiasesOverconfidence); on average, they lose 7.5 cents for every dollar wagered [@Brown2025].
If you are going to bet, only bet a small portion of your money and never more than you are willing to lose.
And do not make multi-leg bets (parlays); people lose on average 25 cents for every dollar wagered on parlays [@Brown2025].
